Validate Structural Analysis \\ \large Testing GPV Method in First-Price Reverse Auctions

### 2020-12-06 paper/paper.tex
add some more

@@

\begin{figure}[h]
    \includegraphics[width=0.8\textwidth]{BidFrequency.png}
    \centering
    \caption{Frequency of normalized bids (bids divided by engineer's estimate)}
    \label{fig:BidFrequency}
\end{figure}

Figure \ref{fig:BidFrequency} plots the frequency of normalized bids. Most bids 
are centered around $110\%$, which is slightly higher than the engineer's estimate 
with respect to which bids are normalized.
However, there are some outliers located in the \textit{More} bin, 
which would cause numeric instability in estimation. 
For data that is More bins, the kernel-estimated bid distribution 
$G_B(\cdot)$ is close to $1$ and so $1-G_B(\cdot)$ close to 0. As in 
the right-hand side of equation (\ref{eqn:ReverseFunction}), the 
part $\frac{g(b)}{1-G_B{b}}$ will tend to infinity as $1-G_B(b)$ 
approaches zero, resulting in the estimated cost to be negative. 
The problem will persist over the boundary of the data and is 
inherent in the kernel distribution estimation.
The boundary-correction technique introduced in \cite{HickmanHubbard2015}
applies only to the kernel density estimation, not kernel 
distribution estimation, and overcoming 
the boundary problems in kernel distribution estimation is outside the scope 
of this paper. For simplicity, therefore, I will first use equation 
(\ref{eqn:ReverseFunction}) to estimate costs and then trim the negative costs.

\subsection{Results}
With data comprised of auctions that have a different number of participants, 
the general estimation procedure remains the same. But the equation 
(\ref{eqn:ReverseFunction}) that assumes a fixed $n$ for the number 
of participants is modified to 
accommodate varying $n$ \cite{Matthewetal2018}
\begin{equation}
    c_{in} = b_{in} - \frac{1}{n-1} \cdot \frac{g(b_{in}|N = n)}{1-G_{B}(b_{in}|N=n)},
    \label{eqn:ReverseFunction_N}
\end{equation}
where $c_{in}$ and $b_{in}$ refer to the cost and bid in $i$-th auction 
with $n$ participants, and the density $g(\cdot|N=n)$ and distribution
$G(\cdot|N=n)$ are estimated on auction data with $n$ participants for 
each $n$ in the dataset.

\begin{figure}[h]
    \includegraphics[width=0.75\textwidth]{cost_bid.jpg}
    \centering
    \caption{Estimated costs plotted against bids.}

    \label{fig:cost_bid}
\end{figure}

Figure \ref{fig:cost_bid} plots the estimated cost against bids in the plot. 
The relationship between costs and bids is almost linear, suggesting that for 
each bid, the inferred cost is very close in terms of numeric values. This is so 
mainly due to the bid distribution. As shown in Figure \ref{fig:BidFrequency}, 
most of the bids are spread in the range [70, 200], which means that for each 
bid $b$, the estimated density value at the specific bid value, $f_c(b)$, is 
small: the peak of $f_c(\cdot)$ being $0.0222$. A closer look at the bid 
distributions of auctions with a different number of participants, $n$, reveals 
that the majority of auction data with small $n$, where the competition is less 
fierce and bidders are able to have a larger markup over the costs than those 
having more competitors, bids are mostly distributed around $110\%$. The 
auctions that more spread-out data, however, have large $n$, in which case 
the markup over costs is decreased due to the competition.

\begin{figure}[h]
\centering
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDensity.jpg}
    \end{minipage}%
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDistribution.jpg}
    \end{minipage}
\caption{Pseudocost density (on the left) and cost distribution (on the right)}
\label{fig:CostEstimation}
\end{figure}

Figure \ref{fig:CostEstimation} shows the kernel-estimated density and 
distribution of pseudo-costs. Because pseudo-costs are close to corresponding 
bids, the density figure on the left of Figure \ref{fig:CostEstimation} is very 
similar to the histogram of bids, Figure \ref{fig:BidFrequency}. As both plots in 
Figure \ref{fig:CostEstimation} show, the inferred costs also center around 
the range [70, 200].

@@

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected for two reasons: 
(1) the test data, which contains an auciton with 16 bidders, does not conform 
to the the bid distribution depicted in Figure \ref{fig:BidFrequency}, and 
(2) I am comparing most likely bids predicted by the estimated cost distribution 
to a particular auction. Therefore, the difference here not suggest the 
inaccuracy of the estimated cost distribution or the equilibrium model. 
Instead, this exercise suggests that we may need to increase the sample size 
to have a more informative comparison.

\section{Conclusion}
This paper tries to propose a way to validate models used in structural analysis 
by cross-validation. The dataset is split into training data and test 
data.
First, this paper has conducted structural estimation on a government 
procurement auction dataset about highway constructions and estimated the 
cost distribution on the training data using a two-step nonparametric procedure.
Second, using the 
estimated cost distribution, the paper then constructs simulated bids with the 
inversion method and compare the simulation to test data. 
(Even though there are no meaningful results yet, it is very likely that 
the two will have statistically significant differences). 
The statistical difference between the simulation and test data suggests that 
the first-price sealed-bid equilibrium model introduced in \citeauthor{RileySamuelson1981} 
\citeyear{RileySamuelson1981} may not be a suitable model to predict bidder's 
behavior in real-world auctions.

However, in the second step of the cross-validation procedure, comparing bids 
directly to test theory's validity may not be a good idea, as suggested in 
\citeauthor{Harrison1989} \citeyear{Harrison1989}. \citeauthor{Harrison1989}
\citeyear{Harrison1989} instead proposes to "evaluate subject behavior in the 
expected payoff space", which can be incorporated into the project's future work.

>>>>

Similar work has been done in \citeauthor{ChernomazYushioto2019} 
\citeyear{ChernomazYushioto2019}, where they have compared the accuracy 
of semiparametric and nonparametric structural estimation methods in an 
asymetric environment.

@@

\begin{figure}
    \includegraphics[width=0.8\textwidth]{BidFrequency.png}
    \centering
    \caption{Frequency of normalized bids (bids divided by engineer's estimate)}
    \label{fig:BidFrequency}
\end{figure}

Figure \ref{fig:BidFrequency} plots the frequency of normalized bids. Most bids 
are centered around $110\%$, which is slightly higher than the engineer's estimate 
with respect to which bids are normalized.
However, there are some outliers located in the \textit{More} bin, 
which would cause numeric instability in estimation. 
For data that is More bins, the kernel-estimated bid distribution 
$G_B(\cdot)$ is close to $1$ and so $1-G_B(\cdot)$ close to 0. As in 
the right-hand side of equation (\ref{eqn:ReverseFunction}), the 
part $\frac{g(b)}{1-G_B{b}}$ will tend to infinity as $1-G_B(b)$ 
approaches zero, resulting in the estimated cost to be negative. 
The problem will persist over the boundary of the data and is 
inherent in the kernel distribution estimation.
The boundary-correction technique introduced in \cite{HickmanHubbard2015}
applies only to the kernel density estimation, not kernel 
distribution estimation, and overcoming 
the boundary problems in kernel distribution estimation is outside the scope 
of this paper. For simplicity, I will first use equation 
(\ref{eqn:ReverseFunction}) to estimate costs and then trim the negative costs.

\subsection{Results}
With data comprised of auctions that have a different number of participants, 
the general estimation procedure remains the same. But the equation 
(\ref{eqn:ReverseFunction}) that assumes a fixed $n$ for the number 
of participants is modified to 
accommodate varying $n$ \cite{Matthewetal2018}
\begin{equation}
    c_{in} = b_{in} - \frac{1}{n-1} \cdot \frac{g(b_{in}|N = n)}{1-G_{B}(b_{in}|N=n)},
    \label{eqn:ReverseFunction_N}
\end{equation}
where $c_{in}$ and $b_{in}$ refer to the cost and bid in $i$-th auction 
with $n$ participants, and the density $g(\cdot|N=n)$ and distribution
$G(\cdot|N=n)$ are estimated on auction data with $n$ participants.

\begin{figure}
    \includegraphics[width=0.75\textwidth]{cost_bid.jpg}
    \centering
    \caption{Estimated costs plotted against bids.}
    \label{fig:cost_bid}
\end{figure}

Figure \ref{fig:cost_bid} plots the estimated cost against bids in the plot. 
Bidder's markup over costs is infinitesimal. This is so 
mainly due to the bid distribution. As shown in Figure \ref{fig:BidFrequency}, 
most of the bids are scattered in the range [70, 200], which means that for each 
bid $b$, the estimated density value at the specific bid value, $f_c(b)$, is 
small: the peak of $f_c(\cdot)$ being $0.0222$. A closer look at the bid 
distributions of auctions with a different number of participants, $n$, reveals 
that the majority of auction data with small $n$, where the competition is less 
fierce and bidders are able to have a larger markup over the costs than those 
having more competitors, has bids compressed around $110\%$. The fact 
that bids and costs are very close also suggests that the auctions are 
very efficient in helping the Colorado government save money.

\begin{figure}
\centering
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDensity.jpg}
    \end{minipage}%
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDistribution.jpg}
    \end{minipage}
\caption{Pseudocost density (on the left) and cost distribution (on the right)}
\label{fig:CostEstimation}
\end{figure}

Figure \ref{fig:CostEstimation} shows the kernel-estimated density and 
distribution of pseudo-costs. Because pseudo-costs are close to corresponding 
bids, the density figure on the left of Figure \ref{fig:CostEstimation} is very 
similar to the histogram of bids, Figure \ref{fig:BidFrequency}. As both plots in 
Figure \ref{fig:CostEstimation} show, the inferred costs also center around 
the range $[70, 200]$. As the density outside the range[70, 200] is very slim, 
the implication will be that simulation based on this cost distribution will not 
be very accurate in generating values outside the range, which partially 
decreases the predictive power of the model.

@@

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected for two reasons: 
(1) the test data, which contains an auciton with 16 bidders, does not conform 
to the the bid distribution depicted in Figure \ref{fig:BidFrequency}, and 
(2) I am comparing most likely bids predicted by the estimated cost distribution 
to a particular auction. Therefore, the difference here not suggest the 
inaccuracy of the estimated cost distribution or the equilibrium model. 
Instead, this exercise suggests that a larger test dataset is needed 
to deliver more informative results.

\section{Conclusion}
This paper tries to propose a way to validate models used in structural analysis 
by cross-validation. The dataset is split into training data and test 
data.
First, this paper conducts structural estimation on a government 
procurement auction dataset about highway constructions and estimates the 
cost distribution on the training data using a two-step nonparametric procedure.
Second, using the 
estimated cost distribution, the paper then constructs simulated bids with the 
inversion method and compare the simulation to test data. 
But the wide difference between the simulation and test data does not suggests
that the first-price sealed-bid equilibrium model introduced in 
\citeauthor{RileySamuelson1981} \citeyear{RileySamuelson1981}
is not a suitable model to predict bidder's 
behavior in real-world auctions. Instead, to draw a firm concludesion requires 
more data.

Moreover, in the second step of the cross-validation procedure, comparing bids 
directly to test theory's validity may not be a good idea, as suggested in 
\citeauthor{Harrison1989} \citeyear{Harrison1989}. \citeauthor{Harrison1989}
\citeyear{Harrison1989} instead proposes to "evaluate subject behavior in the 
expected payoff space", which can be incorporated into future work of the project.
